Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-23 writeup/gz_hubble_data.tex
First draft of text for intro

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\usepackage{url}
\bibliographystyle{mn2e}

@@

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
% $^{4}$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^{5}$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
% $^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
% $^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

\begin{enumerate}
    \item Motivation for studying morphology of galaxies
    \item Particular scientific questions governed by galaxies at $z\sim1$
    \item Theoretical predictions for galaxy morphology evolution
    \item Past imaging and morphology studies at $z\sim1$
    \item Summary of GZ/citizen science work on galaxy morphology to date
\end{enumerate}

\section{Sample and Data} 
\label{sec:data}

@@

\subsection{User weighting}
\label{sec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

\section{Galaxy Zoo interface and classifications}
\label{sec:gz_interface}

@@

\section{Correcting for redshift-dependent classification bias}
\label{sec:debiasing}
The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

@@

\subsection{Correcting GZH morphologies for classification bias}
\label{sec:zeta}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}

\label{fig:features_corrections}
\end{center}
\end{figure}

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}

\label{fig:features_corrections}
\end{center}
\end{figure*}

@@

\subsubsection{TODO LIST}
We need to do: 
\begin{itemize}
\item Calculate the magnitudes, surface brightnesses and sizes of the galaxies in the FERENGI images....
\item Plot of magnitude distribution of galaxies in each of the four GZH subsamples with the magnitudes of our fake galaxies over plotted. 
\item Instructions of how to link the $z=0$ $p_X$ values for galaxies with a given size, magnitude (surface brightness) in the GZH images. 
\end{itemize}

@@

\section{The catalog}

@@

Each image is listed under a unique project ID (eg AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey. For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question. For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
\section{Using the catalog}
\label{sec:cookbook}
Include cookbook for selecting morphologies.

@@

\subfigure{[a]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}

\subfigure{[c]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}

@@

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}

@@

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}

\subfigure{[b]\label{fig:smoothtoint}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}

>>>>

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\usepackage{url}
\bibliographystyle{mn2e}

@@

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as gravitational tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics encoding galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, luminosity, black hole activity, size, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects on the galaxy morphology, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics taking place \citep[for a recent review see][]{con14}.

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individial simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density constrasts dominate down to at least $z\gtrsim$ \citep{gen14}.

Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$. These include spheroids and disks (akin to the ellipticals/spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare, with a very low overall disk fraction \citep{mor13}. Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.

Space-based observatories, particularly the \textit{Hubble Space Telescope}, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{gia04,dav07,gro11,sco07,bec06,wil96} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \textit{HST} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \textit{HST} \citet{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project. GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \textit{Hubble Space Telescope}.

We describe the sample selection and creation of the images used for GZH in Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface and the collection of classifications. Section~\ref{sec:debiasing} outlines the process used to calibrate and ``debias'' the crowdsourced votes. Section~\ref{sec:results} gives the main results as a catalog, with several examples of how the data may be queried in Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview of the observed morphological demographics and compares them to several other catalogs, with a summary in Section~\ref{sec:summary}.

This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.

%\begin{enumerate}
%    \item Motivation for studying morphology of galaxies
%    \item Particular scientific questions governed by galaxies at $z\sim1$
%    \item Theoretical predictions for galaxy morphology evolution
%    \item Past imaging and morphology studies at $z\sim1$
%    \item Summary of GZ/citizen science work on galaxy morphology to date
%    \item Outline of paper
%\end{enumerate}

\section{Sample and Data}\label{sec:data}

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below. The majority of the images (as implied by the project name) are taken directly from \textit{Hubble Space Telescope} Legacy Surveys,

@@

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

\section{Galaxy Zoo interface and classifications}\label{sec:interface}

@@

\section{Correcting for redshift-dependent classification bias}\label{sec:debiasing}

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

@@

\subsection{Correcting GZH morphologies for classification bias}\label{ssec:zeta}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in Figure~\ref{fig:6a}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{center}
\end{figure*}

@@

\subsubsection{TODO LIST}
We need to: 
\begin{itemize}
\item Calculate the magnitudes, surface brightnesses and sizes of the galaxies in the FERENGI images....
\item Plot of magnitude distribution of galaxies in each of the four GZH subsamples with the magnitudes of our fake galaxies over plotted. 
\item Instructions of how to link the $z=0$ $p_X$ values for galaxies with a given size, magnitude (surface brightness) in the GZH images. 
\end{itemize}

@@

\section{The catalog}\label{sec:results}

@@

Each image is listed under a unique project ID (eg AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey. For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question. For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{ssec:weighting}).

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.

\section{Using the catalog}\label{sec:cookbook}
Include cookbook for selecting morphologies.

@@

\subfigure{[a]\label{fig:smooth_to_smooth}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}

\subfigure{[b]\label{fig:smooth_to_int}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}

\subfigure{[c]\label{fig:smooth_to_featured}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}

@@

\subfigure{[b]\label{fig:int_to_smooth}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}

\subfigure{[b]\label{fig:int_to_int}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}

\subfigure{[b]\label{fig:int_to_featured}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}

@@

\subfigure{[b]\label{fig:featured_to_smooth}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}

\subfigure{[b]\label{fig:featured_to_int}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}

\subfigure{[b]\label{fig:featured_to_featured}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}
